 \documentclass[letterpaper, 10pt, draftclsnofoot, onecolumn]{IEEEtran}

\usepackage{graphicx}                                        
\usepackage{amssymb}                                         
\usepackage{amsmath}                                         
\usepackage{amsthm}                                          

\usepackage{alltt}                                           
\usepackage{float}
\usepackage{color}
\usepackage{url}

\usepackage{balance}
\usepackage[TABBOTCAP, tight]{subfigure}
\usepackage{enumitem}
\usepackage{pstricks, pst-node}
\usepackage{supertabular}
\usepackage{url}
\usepackage{fancyhdr}

\usepackage{hyperref}
\usepackage{geometry}

\usepackage{listings}
\usepackage{color}

%\setlength{\parindent}{4em}
%\linespread{1.1}


\def\name{Steven Powers, Josh Matteson, Evan Tschuy}

%pull in the necessary preamble matter for pygments output
%\input{pygments.tex}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {cs461 ``MVP Platform'' Problem Statement},
  pdftitle = {CS 461 Problem Statement},
  pdfsubject = {CS 461 Problem Statement},
  pdfpagemode = UseNone
}



\begin{document}


\begin{titlepage}
\centering
{\huge Many Voices Publishing Platform\par}
{\LARGE Problem Statement\par}
{\vspace{2mm}}
{\large D. Kevin McGrath \& Dr. Kirsten Winters -  CS461 Fall 2016\par}
{\large Steven Powers, Josh Matteson, Evan Tschuy\par}
{\vspace{10mm}}
\begin{abstract}
\noindent  The purpose of the Many Voices Publishing Platform project is to remedy problems 
associated with the current textbook market and standard expectations that come 
with textbooks. The Many Voices Publishing Platform was developed to alleviate 
costs of textbooks for students and provide instructors with the ability 
to create their own. Instructors can use the open platform for collaboration between 
content creators, and other instructors in order to choose the specific focus of their course materials. 
This platform was created using Ward Cunningham's federated wiki as a project 
base and was expanded upon to provide the ability to define and implement a 
collaborative platform for authoring.
\end{abstract}
\end{titlepage}

\vspace{1pc}
\centerline{\sc \large Problem Statement}
\vspace{2pc}

 Today, the textbook industry is filled with yearly updates that are often released with the
minimum number of changes needed to justify a new edition. These textbooks are repeatedly in the range of hundreds of dollars, 
and can be filled with poor or even incorrect information. In the United States, most textbook materials are 
decided by a few states that choose what will appear in textbooks published nation wide. Most professors will
simply choose the book provided to them for review that satisfies their requirements the best, without 
considering the costs that will be passed onto students.
 
Furthermore, the addition of online course materials is used to keep students buying new 
temporary subscription services that used to be free. A professor can either choose a textbook 
from a catalog, one provided for them, or spend months to years writing one of their own. 
If a professor chooses to write their own textbook, they will have to seek publishers,
other contributors, and have their work peer reviewed before it can finally be released to store shelves. 
If a professor chooses a book through a catalog or one provided for them, the pre-written textbooks 
often contain unnecessary chapters, or can even be missing key sections on topics viewed as critical. This can further result in 
additional class materials being purchased by students to supplement the missing information. \\

 The Many Voices platform instead allows professors to create their own textbooks 
by using crowd-sourced content. Content creators are able to submit materials of 
all different formats, including: images, small pieces of text, pages, or even entire chapters. 
The submitted materials are able to be reviewed by editors and other contributors to prevent invalid 
materials from being used.
A knowledgeable professor can contribute a chapter or unit on their specialty, and 
others are able to modify the obtained materials in the way they see fit. These materials may be
offered for free or for a nominal fee, determined by the content creator.

Once materials are acquired, anyone is able to create a more affordable textbook available in either
a downloadable ebook or in printed form to create the exact textbook they want for their classes
or for any purpose they desire. These materials are able to be hosted on a version control 
website such as GitHub, that allow for users to fork and branch their changes to satisfy their goals.
Additionally the platform will feature a way for editors to review content, and moderate changes in a manner similar
to the approach Wikipedia has for high conflict pages, restricting who can edit for very popular pages.

The platform will also feature a way to search for and find documents relevant to the users interests. 
Through a variety of search criteria, the requested topic or subject will turn up results prioritized by
relevance and credibility. By default, the platform will offer the most used and/or reviewed materials
based on entered search terms. Users will be able to narrow down their options by specifying date ranges,
certain contributors, editor review score, and more choices to make finding the right document an easy process.
The finished platform will allow users to see existing 
textbooks, customize them using their own or third party materials, and contribute their 
customizations back to other professors. \\

The platform will be viewed as a success if the platform allows instructors to submit, edit, publish, 
and compile materials for the creation of textbooks and other instructional materials. 
Our goal is to ensure the platform meets our clients project expectations, the defined needs,
and functions as according to our development plan. We will, in our best efforts, plan to meet at 
minimum every two weeks with our client to discuss current progress of project goals and 
proposed functionality for the application. 
Finally, before beginning work on major project milestones and certain aspects of the platform, we will 
discuss the overall status of the project. We will further inquire as to whether our client has any additional insight to assist in 
meeting project expectations as desired. After reaching a reasonable agreement, we will continue to adjust 
and shape the platform where necessary. We will further ensure that the development taking place on
the platform is to the best of our abilities. \\


\newpage
\centerline{\sc \large Signature Page}
\vspace{5pc}


\centering

\begin{tabular}{lllll}
Carlos Jensen, Client    & \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ & Date & \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ &  \\
                         &                                                                                  &      &                                            &  \\
Steven Powers, Developer & \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ & Date & \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ &  \\
                         &                                                                                  &      &                                            &  \\
Josh Matteson, Developer & \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ & Date & \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ &  \\
                         &                                                                                  &      &                                            &  \\
Evan Tschuy, Developer   & \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ & Date & \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ &  \\
                         &                                                                                  &      &                                            & 
\end{tabular}


\end{document}
