\documentclass[onecolumn, draftclsnofoot,10pt, compsoc]{IEEEtran}

\usepackage{supertabular}
\usepackage{tabu}

\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyfoot[C]{REQCHANGE--\thepage}
\begin{document}
\section{What Requirements Changed?}

Throughout development of the Many Voices Publishing Platform, only a few changes were made throughout development that strayed from the original requirements and planning.

\begin{flushleft}
	\tablehead{}
	\begin{supertabular}{|p{0.5cm}|p{3cm}|p{5.5cm}|p{7cm}|}
		\hline
		 & Requirement & Description of What Happened & Comments
		\\\hline
		1 & Operated via website & The product is to be operated via a website for wide availability and use & A website was used to demonstrate and allow for users to use the product.
		\\\hline
		2 & Provide tools needed for textbook creation & The product will give the tools necessary for individual professors to create the textbook they need to match their desires & The product provides a variety of tools that facilitate the creation of a textbook with new or already existing materials that the user can combine in any way they see fit.
		\\ \hline
		3 & Document creation service & The product will be a document construction service  &  The product allows for the creation of documents.
		\\ \hline
		4 & Use of pre-existing materials & The product will allow for the creation of a textbook out of pre-existing materials (chapters / scraps), by searching and selecting from a list & The product allows for the use of pre-existing materials by searching and selecting. Also included is the ability to drag and drop selection.
		\\ \hline
		5 & LaTeX Support & The product will support the use of LaTeX within scraps & The product allows the user to enable LaTeX support when creating / editing a scrap.
		\\ \hline
		6 & Media Support & The product will support the use of media, such as images or perhaps video content & The product supports the use of images when creating a scrap.
		\\ \hline
		7 & Modern Design Paradigms & The product will be graphically driven by using a design philosophy such as Google's Material Design & The product employs the use of Materialize for the graphical user interface.
		\\ \hline
		8 & Security Barrier & The inter-process communication should be handled in a generic way that provides a high-security barrier, preventing malicious users from accessing other, non-specified applications & The product uses Google OAuth for user login and transmission of data and the product runs within a container, preventing external manipulation.
		\\ \hline
		9 & Will be a fork of Ward Cunningham's Federated Wiki & The product will use Ward Cunningham's Federated Wiki as the starting point for development & The product does not use Ward Cunningham's Federated Wiki as the base starting point. During development, a lot or problems surfaced from the lack of polish and features present within the Federated Wiki. Development started from the ground up instead.
		\\ \hline
		10 & Database & The product will use a database such as CouchDB 2.0, PostgresSQL, etc  & The product features a backend Mongo Database.
		\\ \hline
		11 & Passwords & Passwords shall be stored in a securely hashed, non-reversible method, such that infiltration of the product by an unauthorized third party will not be able to result in the theft of user passwords & The product does not store any user passwords in any regards, and relies on Google OAuth for user authentication instead.
		\\ \hline
		12 & Performance \& Compatibility & The product shall aim for 100 simultaneous users, as well as 95\% uptime and usability. Additionally maintain 99.99\% accessibility from major browsers & The final product does not promise specific response times, browser compatibility percentages, but maintains compatibility with the major web browsers.
		\\ \hline
		13 & Training Materials & The product will not feature any additional training materials beyond limited help screens built into the software and accompanying user manual & The product features tool tips instead of help screens.
		\\ \hline
		
		14 & Web Frontend using JavaScript & The product will use a JavaScript or JavaScript variant for the web frontend & The product uses the Aurelia JavaScript framework for the frontend.
		\\ \hline
		
		15 & User Interfaces & The product will use Angular2 for a Single Page Application or similar variant & The product uses Aurelia for the single page application instead of Angular2.
		\\ \hline
		
		16 & Compile A Book & Ability to compile a book, with search functionality for finding existing textbooks, ability to duplicate and edit existing textbooks, and add a new blank textbook & The product allows the user to search for existing materials, including textbooks, the ability to remix (fork and duplicate) a book, and create a new textbook.
		\\ \hline
		
		17 & Textbook Compilation Interface & Ability to edit / create a new chapter, a 'table of contents' view with access to editing. Button to add new scrap to a chapter, ability to search scraps, and user-friendly interface to add scrap to the desired location. & The product features a way edit and create new chapters, view a books 'table of contents' that allows the user to quickly edit or create a new chapter, and within editing a chapter, being able to edit or create a new scrap. The user also has the ability to arrange the chapters / scraps in the order they please. The product also features a user-friendly interface.
		\\ \hline
		
		18 & Search & The product will feature a way to search for relevant materials based on keyword, author, tag, field, ranked by relevance and/or community voting. Scrap, Chapter, Textbook searching & The product features a way to search for relevant materials based on keywords within a material, specific words applied with tags, that are automatically ranked by relevance. Being able to search by author is limited, because the end user is able to change their username. 
		\\ \hline
		
		19 & Publishing Interface & The product will support the ability to save the textbook as a PDF / send the textbook to the printer. & The product features a way to preview the textbook in browser at the click of a button, or the user can view the textbook externally with the viewer of their choice. This allows the user to print the textbook if they desire.
		\\ \hline
		
		20 & Scrap Editor & The product will feature a 'pretty' view for adding formatted text, media, etc, to a scrap, and a 'raw' view for managing scrap ordering. Additionally tag management for a scrap. & The product features the ability to add LaTeX formatted text, or upload and add an image to a scrap. There is no 'pretty' and 'raw' view and instead both are seamlessly integrated.
		\\ \hline
		
		%4 & REQ & Description & 
		%\\ \hline
	\end{supertabular}
\end{flushleft}


\end{document}